### 2024-09-02 manuscript.tex
Inclusive years

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/map_fig.pdf}
\caption{
\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
analysed here. The tracks cover Antarctic sectors south of South America, the
Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010 to 2021.
The dotted and dashed lines at 40°S and 55°S delineate the Southern
Ocean area of our analysis and its partitioning into two subsets, respectively.
A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
CL51 installation at the Macquarie Island station (© Jeﬀ Aquilina, Bureau of
Meteorology).
% TODO: Ask for photo permission and info about license.
}
\label{fig:map}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cyc_dist.pdf}
\caption{
Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
2010--2013 and \textbf{(b)} ICON in model years 2021--2023 (free running) as
identified by CyTRACK, expressed as a fraction of the number of days with
cyclonic activity, defined as grid points located within a double radius of any
cyclone on a given day (UTC).
}
\label{fig:lts}
\end{figure}

@@

A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
by the nextGEMS project \citep{hohenegger2023}. nextGEMS has so far produced
four cycles of model runs. In our research, we used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}. We could
not use Cycle 4 due to unavailability of the necessary variables. The
horizontal resolution of ngc3028 is about 5 km.  Unlike current general
circulation models (GCMs), the strom-resolving version of ICON does not use
convective and cloud parameterisation but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterisations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterised in this model. In our analysis, we used
four years of coupled simulation output between years 2021 and 2024
(inclusive). Because the model is free-running, weather and climate
oscillations (such as the El Niño--Southern Oscillation) are not expected to be
equivalent to reality at the same time and place. To compare with observations
taken during different years (2010--2021), we compared the model output with
observations at the same time of year and geographical location.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/map_fig.pdf}
\caption{
\textbf{(a)} A map showing the tracks of 31 voyages of RV \emph{Polarstern},
RSV \emph{Aurora Australis}, RV \emph{Tangaroa}, RV \emph{Nathaniel B. Palmer},
and HMNZS \emph{Wellington} and one sub-Antarctic station (Macquarie Island)
analysed here. The tracks cover Antarctic sectors south of South America, the
Atlantic Ocean, Africa, Australia, and New Zealand in the years 2010--2021
(inclusive).  The dotted and dashed lines at 40°S and 55°S delineate the
Southern Ocean area of our analysis and its partitioning into two subsets,
respectively.  A photo of \textbf{(b)} RV \emph{Polarstern} (© Folke Mehrtens,
Alfred-Wegener-Institut), \textbf{(c)} Lufft CHM 15k installed on RV
\emph{Tangaroa} (© Peter Kuma, University of Canterbury), \textbf{(d)} Vaisala
CL51 installation at the Macquarie Island station (© Jeﬀ Aquilina, Bureau of
Meteorology).
% TODO: Ask for photo permission and info about license.
}
\label{fig:map}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cyc_dist.pdf}
\caption{
Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
2010--2013 (inclusive) and \textbf{(b)} ICON in model years 2021--2023 (free
running) as identified by CyTRACK, expressed as a fraction of the number of
days with cyclonic activity, defined as grid points located within a double
radius of any cyclone on a given day (UTC).
}
\label{fig:lts}
\end{figure}

@@

A coupled (atmosphere--ocean) GSRM version of the ICON model is in development
by the nextGEMS project \citep{hohenegger2023}. nextGEMS has so far produced
four cycles of model runs. In our research, we used a Cycle 3 run
\emph{ngc3028} produced in 2023 \citep{nextgems2023a,nextgems2023b}. We could
not use Cycle 4 due to unavailability of the necessary variables. The
horizontal resolution of ngc3028 is about 5 km.  Unlike current general
circulation models (GCMs), the strom-resolving version of ICON does not use
convective and cloud parameterisation but relies on explicit simulation of
convection and clouds on the model grid. While this makes the code development
simpler without having to rely on uncertain parameterisations, it can miss
smaller-scale clouds below the grid resolution.  Turbulence and cloud
microphysics are still parameterised in this model. In our analysis, we used
four years of coupled simulation output between years 2021 and 2024
(inclusive). Because the model is free-running, weather and climate
oscillations (such as the El Niño--Southern Oscillation) are not expected to be
equivalent to reality at the same time and place. To compare with observations
taken during different years (2010--2021, inclusive), we compared the model
output with observations at the same time of year and geographical location.
